---
title: "International cooperation"
author: "L.-Y. M."
date: "2024-02-14"
output: html_document
---

```{r setup, include=FALSE}
library("tidyverse")
library("ggExtra")
library("scattermore")
library("cowplot")
```

## R Markdown

Reference: Lin, Y., Frey, C. B., & Wu, L. (2023). Remote collaboration fuses fewer breakthrough ideas. Nature, 623(7989), 987–991. <https://doi.org/10.1038/s41586-023-06767-1>

The raw date used in this project can be found in <https://lyl010.github.io/>.

```{r data input}
dataset1 <- read_csv("raw data/Paperid_Remoteness_Authors_Teamroles.csv")
city_latlong <- read_csv("raw data/ScienceCityLatLong.csv")
paperid_year <- read_delim("raw data/Paperid_Year_Discipline_Teamsize_Distance_Dscore.txt", col_names = c("Paperid","Year","Discipline","Teamsize","Distance","Dscore"), delim = "\t")
dataset2 <- read_delim("raw data/ScienceDisruptionCityEdges.txt", col_names = 
                         c("Connection","color","main_city","D_score1","D_score2"), delim = "\t")
dataset5 <- read_csv("raw data/Paperid_Remoteness_Authors_Teamroles.csv")
```

## Prepare data

You can also embed plots, for example:

```{r data reshaping}
connection_data <- dataset2 %>% 
  unite(D_score,c("D_score1","D_score2"),sep = ",")

science_and_engineering = c("geology","medicine","mathematics","physics","materials science",
                            "biology","chemistry","engineering","computer science","geography",
                            "environmental science")
social_sciences <- c("political science","business","economics","psychology","sociology")
art_and_humanity <- c("history","art","philosophy")

df <- bind_rows(
  data.frame(Discipline = science_and_engineering, fields = "science_and_engineering"),
  data.frame(Discipline = social_sciences, fields = "social_sciences"),
  data.frame(Discipline = art_and_humanity, fields = "art_and_humanity")
)

paperid_year <- left_join(paperid_year, df, by = "Discipline")
```

```{r top1%}

top_paper <- paperid_year %>% 
  filter(Dscore > 0.2)


ds_hist <- ggplot(top_paper, aes(x = Dscore))
ds_hist + geom_histogram()

ds_n0_hist <- ggplot(top_paper %>% filter(Distance > 0), aes(x = Dscore))
ds_n0_hist + geom_histogram()

di_hist <- ggplot(top_paper, aes(x = Distance))
di_hist + geom_histogram()

di_n0_hist <- ggplot(top_paper %>% filter(Distance > 0), aes(x = Distance))
di_n0_hist + geom_histogram()

d_d <- ggplot(top_paper, aes(x = Distance, y = Dscore, color = Year)) +
  geom_point(alpha = 0.1)
#  geom_scattermore() # otherwise, it can take forever
ggMarginal(d_d, type = "histogram")

d_d_n0 <- ggplot(top_paper %>% filter(Distance > 0), aes(x = Distance, y = Dscore, color = Year, shape = fields)) +
  geom_point(alpha = 0.1) + theme_cowplot()
ggMarginal(d_d_n0, type = "histogram")

frequency_Dscore <- top_paper %>% 
  group_by(Dscore) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n))

# filter out the few cited papers (extremely frequent Dscore)
ex_lc <- left_join(top_paper, frequency_Dscore, by = "Dscore") %>% 
  filter(n < 1000) # that is an arbitrary threshold

d_d_n0_without_few_cited <- ggplot(ex_lc %>% filter(Distance > 0), 
                                   aes(x = Distance, y = Dscore, color = Year)) +
  geom_point(alpha = 0.1) + theme_cowplot() +
  theme(legend.position = "left")
ggMarginal(d_d_n0_without_few_cited, type = "histogram")

```

```{r log scale}

d_d_n0_log <- d_d_n0 + scale_x_continuous(trans = 'log10') + # Log scale for x-axis
  scale_y_continuous(trans = 'log10') # Log scale for y-axis
ggMarginal(d_d_n0_log, type = "histogram")
```

```{r distribution of Dscore in local}
Locol_data <- paperid_year %>% 
  filter(Distance == 0)
ds_hist_l <- ggplot(Locol_data, aes(x = Dscore))
ds_hist_l + geom_density()
```

The resason why distance is extremly right-skewed might be that those papers are demestic collaboration. It is impossible to investigate the affect of demestic / international collaboration on the Dscore due to the data lack of that information. However, we can use distance as a proxy of demestic / international collaboration. 
According SJR, Germany is top 4 country which published most paper and has a medium territory area, that is 357,021 km2. Let's assume that it is a circle, then the radius is 337 km. We can use this value as a threshold to distinguish demestic and international collaboration.


```{r data of demestic collabo}
d_d_deme <- ggplot(top_paper %>% filter(Distance < 337), aes(x = Distance, y = Dscore, color = Year, shape = fields)) +
  geom_point(alpha = 0.1) + theme_cowplot()
ggMarginal(d_d_deme, type = "histogram")

d_d_deme_n0 <- ggplot(top_paper %>% filter(Distance < 337) %>% filter(Distance > 0), 
                      aes(x = Distance, y = Dscore, color = Year, shape = fields)) +
  geom_point(alpha = 0.1) + theme_cowplot()
ggMarginal(d_d_deme_n0, type = "histogram")

```

```{r data of international collaboration}
d_d_inte <- ggplot(top_paper %>% filter(Distance > 700), aes(x = Distance, y = Dscore, color = Year, shape = fields)) +
  geom_point(alpha = 0.1) + theme_cowplot()
ggMarginal(d_d_inte, type = "histogram")
```

That is a Laplace distribution
